Stochastic Newton with Arbitrary Sampling

### 2023-05-03 paper/Stochastic Newton with Arbitrary Sampling.tex
Fixed paper
Fix paper

	The problem of minimizing the average of a large number of sufficiently smooth and strongly convex functions is ubiquitous in machine learning. Stochastic first-order methods for this problem of Stochastic Gradient Descent type are well studied. In turn, second-order methods, such as Newton, have certain advances since they can adapt to the curvature of the problem. They are also known for their fast convergence rates. But stochastic variants of Newton-type methods are not studied as good as SGD-type ones and have limitations on the batch size. Previously, a method was proposed which requires no limitations on batch sizes. Our work explores this method with different sampling strategies that lead to practical improvements.

>>>>

	The problem of minimizing the average of a large number of smooth and strongly convex functions is ubiquitous in machine learning. Stochastic first-order methods for this problem of Stochastic Gradient Descent type are well studied. In turn, second-order methods, such as Newton, have certain advances since they can adapt to the curvature of the problem. They are also known for their fast convergence rates. But stochastic variants of Newton-type methods are not studied as good as SGD-type ones and have limitations on the batch size. Previously, a method was proposed which requires no such limitations. Our work explores this method with different sampling strategies that lead to practical improvements.
